MLH1 data report 

### 2017-10-13 rmd_report.rmd
updated from work

ply_data <- df.pasd.mice[df.pasd.mice$mouse == "8oct14_PWD_f8",]

#make this the function that I apply over the mice in the data
t.test(sample(ply_data$nMLH1.foci, 5), sample(ply_data$nMLH1.foci, 5))$p.value
t.test(sample(ply_data$nMLH1.foci, 13), sample(ply_data$nMLH1.foci, 13))$p.value

>>>>

ply_data <- df.pasd.mice[df.pasd.mice$mouse == "8oct14_PWD_f8",]
#make this the function that I apply over the mice in the data

#simplify the t.test
t.test(sample(ply_data$nMLH1.foci, 5), sample(ply_data$nMLH1.foci, 5))$p.value
t.test(sample(ply_data$nMLH1.foci, 13), sample(ply_data$nMLH1.foci, 13))$p.value

#repeat the sampling 100 times

bb <-ddply(jj, .(mouse), function(x) t.test(x[1,2:5],x[2,2:5])$p.value )#t.test for 2

#try with do
blah <- df.pasd.mice %>% group_by(mouse) %>% do(head(.))

plist=data.frame(pv=as.numeric(), mean1=as.numeric(), mean2=as.numeric())

hundred <- function(x){
  plist=data.frame(pv=as.numeric(), mean1=as.numeric(), mean2=as.numeric())
  for(eye in 1:100){
    samp1 = sample(x, 5)
    samp2 = sample(x, 5)
    plist$pv[eye] <- t.test(samp1,samp2)$p.value
    plist$mean1[eye] <- mean(samp1)
    plist$mean2[eye] <- mean(samp2)
  }
  return(plist)
}

mm <- hundred(ply_data$nMLH1.foci)
